---
title: "Getting Started with DBmaps"
author: "Sagar Udasi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with DBmaps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(DBmaps)
```

# Introduction

DBmaps simplifies the analysis of relational database structures by automating table merging operations. This vignette demonstrates the package's core functionality for merging multiple tables efficiently.

## Installation

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("I-am-Sagar/DBmaps", build_vignettes = TRUE)
```

# Merging Tables with DBmaps

The `merge_all_tables()` function allows you to merge three tables in one operation. Here's how to use it:

```{r example}
# Load sample data
data(students)
data(scores)
data(attendance)

# Perform a three-way merge
result <- merge_all_tables(
  students, 
  scores, 
  attendance,
  by_col = "id",
  merge_type = "inner",
  final_merge_type = "inner"
)

head(result)
```

# Best Practices

1.  Verify unique identifiers in your key columns
2.  Check for NA values in final dataset
3.  Consider merge order for optimal results

# Session Info

```{r session_info}
sessionInfo()
```
